### 2025-07-17 manuscript/part2.tex
Extension points

  \item[\texttt{checkArrayAccess (Lval)}]
    Infers the index expression’s type; reports on conflicting inconsistencies\textsuperscript{*} detected during type inference, or if it is not an integer.

@@

\section{VS Code Extension Points}
textmate highlighting lang-config.json
\section{Testing}
\section{Parsing Speed}

>>>>

  \item[\texttt{checkArrayAccess (Lval)}]
    Infers the index expression's type; reports on conflicting inconsistencies\textsuperscript{*} detected during type inference, or if it is not an integer.

@@

\section{VS Code Extension Points}
textmate highlighting lang-config.json

??maybe ref from the firt mention of the extension (structure)

The changes made to the files associated with the extension's build are minimal yet essential. The extension's entry point remains \code{main.ts} in the
\code{extension/} directory, while \code{tmLanguage.json} serves as the primary configuration for syntax highlighting, specifying the label and groups used to color tokens.
During the build pipeline (invoked by \code{npm run ...}), a small custom script reads \code{tmLanguage.json}, injects the necessary snippets (\ref{list:customsyntax})
that aren't included by default, and writes the updated file back so that our custom tokens are recognized and styled correctly.

\begin{minted}[bgcolor=lightgray, frame=lines, breaklines, linenos]{json}
  {
    "name": "storage.type.int-prefix.mini-prob",
    "match": "\\b[su][1-9][0-9]*\\b"
  },
  {
    "name": "keyword.control.boolValue.mini-prob",
    "match": "\\b(true|false)\\b"
  }
\end{minted}
\captionof{listing}{Patched syntax configurations}
\label{list:customsyntax}
\vspace{0.5em}

Another critical component is \code{esbuild.js}, which handles transpiling TypeScript into JavaScript, bundling and minifying dependencies, and resolving imports so
that both the "extension main" and "language main" entry points become single \code{.js} modules. VSCE, the CLI used to package \code{.vsix} files, requires CommonJS
modules, but the repository is set to ESM (\code{"type": "module"}), so we updated the \code{package.json} entries in \code{out/extension/main.js} and
\code{out/language/main.js} to force a CommonJS output. This adjustment not only silenced VSCE's bundling warnings but - by bundling the files through
\code{esbuild.js}-reduced the package footprint from about 27MB of loose output down to roughly 1MB in the final \code{.vsix}.

\section{Testing}
\section{Parsing Speed}
